### 2021-01-06 Paper/results.tex
new script

{\color{red}
\paragraph{Influence of the subsignals length $M$}
To evaluate the forecasting quality, {\sf SigExt} is applied to $1000$ realizations of the above-described signal. Here, we forecast signal extensions of $0.1$~s, \ie~$L=700$. Besides, we set $K=2625$. Table~\ref{tab:mse.sine} shows the resulting experimental MSE according to four  different selected values of the subsignals length $M$.

}

\paragraph{Comparison of the extensions methods}
The same set of experiments is run on the extension methods outlined in section~\ref{sse:methods}. For comparison, the mean and the standard deviation (SD) of the resulting MSEs are given in Table~\ref{tab:mse.sine}. They show that the naive extension we propose gives satisfying results, in particular in comparison with the point-symmetric extension. Besides, even though the other more sophisticated methods, like GPR, give MSE values that have a slightly smaller standard deviation, these methods are substantially limited by the computing time they require, which prevents them from being used to exploit real-time data. Thus, {\sf SigExt} is the extension method that optimizes the trade-off between forecasting quality and computing time.

\begin{table}
\centering
\caption{AHM Signal: Performance of the Extension Methods}
\begin{tabular}{|c||c|c|}
  \hline
   \multirow{2}{60pt}{\centering Extension method} & \multirow{2}{50pt}{\centering MSE\\ (mean $\pm$ SD)}  & \multirow{2}{80pt}{\centering Averaged computing time (seconds)} \\
    &  & \\
   \hhline{|=#=|=|}
   {\sf SigExt ($M=100$)} & $1.028 \pm  0.404$ & $1.069$ \\
   \hline
   {\sf SigExt ($M=750$)} & $1.028 \pm  0.404$ & $1.069$ \\
   \hline
   {\sf SigExt ($M=1500$)} & $1.028 \pm  0.404$ & $1.069$ \\
   \hline
   {\sf SigExt ($M=3000$)} & $1.028 \pm  0.404$ & $1.069$ \\
   \hline
   Symmetric & $4.368 \pm  0.001$ & $0.001$ \\
   \hline
   EDMD & $1.156  \pm  0.003$ &$11.10$\\
   \hline
   GPR & $1.025  \pm  0.403$ &$244.7$ \\
   \hline
   TBATS & $1.501 \pm  1.354$ & $633.6$ \\
   \hline
\end{tabular}
\label{tab:mse.sine}
\end{table}

>>>>

{\color{red}
\paragraph{Influence of the subsignals length $M$}
To evaluate the forecasting quality, {\sf SigExt} is applied to $1000$ realizations of the above-described signal. We forecast signal extensions of $0.1$~s, \ie~$L=700$. Table~\ref{tab:mse.sine} shows the resulting mean and standard deviation (SD) of the experimental MSE, according to four different values of the subsignals length $M$. Note that choosing a too small value for $M$ does not provide enough information to forecast the signal satisfactorily. Furthermore, a value of $M$ that is too large makes the algorithm insensitive to local nonstationarities produced by frequency variations. The user must then make a compromise on the choice of $M$ in order to optimize the performance of the algorithm. A choice of $M$ such that the subsignals contain about a dozen oscillations is generally appropriate.
}

\paragraph{Comparison of the extensions methods}
The same set of experiments is run on the extension methods outlined in section~\ref{sse:methods}. The results, displayed in Table~\ref{tab:mse.sine}, show that the naive extension we propose gives satisfying results, in particular in comparison with the point-symmetric extension. Besides, even though the other more sophisticated methods, like GPR, give MSE values that have a slightly smaller standard deviation, these methods are substantially limited by the computing time they require, which prevents them from being used to exploit real-time data. Thus, {\sf SigExt} is the extension method that optimizes the trade-off between forecasting quality and computing time. {\color{red} Besides, the last column of Table~\ref{tab:THO} gives the performance index $D$ of the boundary-free STFT associated with each extension method. This illustrates the ability of our algorithm to reduce boundary effects to a level comparable to what is possible with the GPR or TBATS extensions. The performance of {\sf BoundEffRed} on other TF representations is more thoroughly analyzed on real-life signals in the following.}

\begin{table}
\centering
\caption{AHM Signal: Performance of the Extension Methods and the Associated Boundary-Free STFT}
\begin{tabular}{|c||c|c||c|}
  \hline
   \multirow{2}{60pt}{\centering Extension method}  & \multirow{2}{30pt}{\centering CPU time (s)} & \multirow{2}{50pt}{\centering MSE\\ (mean $\pm$ SD)} & \multirow{2}{50pt}{\centering Index $D$ of the STFT}\\
    &  & & \\
   \hhline{|=#=|=#=|}
   {\sf SigExt ($M=100$)} & $0.008$ & $1.133 \pm  0.077$ & \\
   \hline
   {\sf SigExt ($M=750$)} & $0.122$ & $0.479 \pm  0.166$ & \\
   \hline
   {\sf SigExt ($M=1500$)} & $0.634$ & $0.907 \pm  0.377$ & \\
   \hline
   {\sf SigExt ($M=3000$)} & $2.881$ & $5.365 \pm  3.919$ & \\
   \hline
   Symmetric &  {\color{red}$<0.001$} & {\color{red}$4.368 \pm  0.001$} &\\
   \hline
   EDMD & {\color{red}$11.10$} & {\color{red}$1.156  \pm  0.003$} & \\
   \hline
   GPR & {\color{red}$244.7$} & {\color{red}$1.025  \pm  0.403$} &\\
   \hline
   TBATS  & {\color{red}$633.6$} & {\color{red}$1.501 \pm  1.354$} & \\
   \hline
\end{tabular}
\label{tab:mse.sine}
\end{table}
